Parameterized convection, stratiform clouds and resolution sensitivity in the Community Atmosphere Model

### 2019-08-23 resolution.tex
edits

Through approximating the cloud base as the $850$ hPa level, equation~\ref{eq:mflux} was found to be a good approximation to total precipitation rates in a regional model \citep{RETAL2016CD} and in the CAM-SE AGCM with CAM5 physics, across multiple resolutions \citep{OETAL2016JAMES}. Figure~\ref{fig:mflux} shows the median convective, stratiform and total precipitation rates conditioned on the $850$ hPa moisture flux using $1$ mm/day bins, in the CAM6 $ne30$ simulation. The figure shows that the moisture flux is a good approximation to the median total precipitation rate, and that the increase in precipitation rates with moisture flux is primarily from the stratiform precipitation scheme.

>>>>

Through approximating the cloud base as the $850$ hPa level, equation~\ref{eq:mflux} was found to provide to provide a good fit to total precipitation rates in a regional model \citep{RETAL2016CD} and in the CAM-SE AGCM with CAM5 physics, across multiple resolutions \citep{OETAL2016JAMES}. Figure~\ref{fig:mflux} shows the median convective, stratiform and total precipitation rates conditioned on the $850$ hPa moisture flux using $1$ mm/day bins, in the CAM6 $ne30$ simulation. The figure shows that the moisture flux is a good approximation to the median total precipitation rate, and that the increase in precipitation rates with moisture flux is primarily from the stratiform precipitation scheme.
